$\pi$ with leftovers: \\ a mechanisation in Agda

### 2021-01-25 paper/paper.tex
Update paper.tex
one always escapes
Rearrenge first example listings

\documentclass[]{llncs}
% TODO: get rid of page numbers
\pagestyle{plain}

\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{amsmath}
\usepackage{mathbbol}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{appendix}

@@

\renewcommand{\sectionautorefname}{\S}%
\renewcommand{\subsectionautorefname}{\S}%
\renewcommand{\appendixautorefname}{Appendix}

@@

The \sender{} and \receiver{} \emph{roles} are defined below, parametrised by the channels on which they operate.
The \sender{} creates a new channel to be sent as data, and sends it over channel $c$, and then terminates.
Each \sender{} process $\func{send} \, x$ and $\func{send} \, y$ is an instantiation of $\func{send} \, c$.
The \receiver{} receives data \emph{twice} on a channel $c$ and then terminates.
The \receiver{} process $\func{recv} \, z$ is an instantiation of $\func{recv} \, c$.
\todo{get rid of vertical space}
\begin{minipage}[t]{0.5\textwidth}
\begin{flalign*}
  & \func{send} \; : \; \Var_n \to \Process_n & \\
  & \func{send} \; c = \new{} \send{(\suc c)}{\constr{0}} \PO
\end{flalign*}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\begin{flalign*}
  & \func{recv} \; : \; \Var_n \to \Process_n & \\
  & \func{recv} \; c \; = \recv{c}{} \recv{(\suc c)} \PO
\end{flalign*}
\end{minipage}

The \courier{} role is defined below as $\func{carry} \; x \; y \; z$.
It sequentially receives on the two input channels $x$ and $y$ -- instantiating $in0$ and $in1$, and then outputs the two pieces of received data on the output channel $z$ -- instantiating $out$.
Finally, we create three communication channels and compose all four processes together: the first channel is shared between the one \sender{} and the \courier{}, the second between the other \sender{} and the \courier{}, and the third between the \receiver{}  and the \courier{}.
The result is the courier $\func{system}$ defined below.
\begin{minipage}[t]{0.5\textwidth}
\begin{flalign*}
  \func{carry} \; : \; \Var_n \to \Var_n \to \Var_n \to \Process_n%
\end{flalign*}%
\begin{flalign*}
  & \func{carry} \; in0 \; in1 \; out \; &&= \\
  & && \recv{in0 &&}{} \\
  & && \recv{(\suc \; in1) &&}{} \\
  & && \send{(\suc \suc \; out) &&}{\suc \constr{0}} \\
  & && \send{(\suc \suc \; out) &&}{\constr{0}} \PO
\end{flalign*}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\begin{flalign*}
  & \func{system} && : \; \Process_{\constr{0}} & \\
  & \func{system} && = \new{} ( \func{send} \; \constr{0} \\
  & && \comp{}{ \new{} ( \func{send} \; \constr{0} } \\
  & && \comp{}{ \new{} ( \func{recv} \; \constr{0} } \\
  & && \comp{}{ \func{carry} \; (\suc \suc \constr{0}) \; (\suc \constr{0}) \; \constr{0}))) } \\
\end{flalign*}
\end{minipage}
\todo{fix}

@@

\bibliographystyle{splncs04}
\bibliography{paper}

%%
\appendix
\input{appendix.tex}
\end{document}

>>>>

\documentclass[runningheads]{llncs}
% TODO: get rid of page numbers

\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{amsmath}
\usepackage{mathbbol}
\usepackage{mathtools}
\usepackage{hyperref}
\usepackage{todonotes}
\usepackage{appendix}
\usepackage[strict]{changepage}

@@

%% remove for the camera ready
\AtBeginDocument{%
\renewcommand*{\figureautorefname}{Fig.\@\!}
\renewcommand*{\sectionautorefname}{\S\!\!\,}
\renewcommand*{\subsectionautorefname}{\S\!\!\,}
\newcommand*{\nitheoremautorefname}{Thm.}
\newcommand*{\nidefinitionautorefname}{Def.}
\newcommand*{\nilemmaautorefname}{Lem.}
\newcommand*{\exampleautorefname}{Eg.}
}

@@

The \sender{} and \receiver{} \emph{roles} are defined below, parametrised by the channels on which they operate.
The \sender{} creates a new channel to be sent as data, and sends it over channel $c$, and then terminates.
Each \sender{} process $\func{send} \, x$ and $\func{send} \, y$ is an instantiation of $\func{send} \, c$.
The \receiver{} receives data \emph{twice} on a channel $c$ and then terminates.
The \receiver{} process $\func{recv} \, z$ is an instantiation of $\func{recv} \, c$.
\begin{align*}
  & \func{send} \; c = \new{} \send{(\suc c)}{\constr{0}} \PO &&
    \func{recv} \; c \; = \recv{c}{} \recv{(\suc c)} \PO
\end{align*}

The \courier{} role is defined below as $\func{carry} \; x \; y \; z$.
It sequentially receives on the two input channels $x$ and $y$ -- instantiating $in0$ and $in1$, and then outputs the two pieces of received data on the output channel $z$ -- instantiating $out$.
Finally, we create three communication channels and compose all four processes together: the first channel is shared between the one \sender{} and the \courier{}, the second between the other \sender{} and the \courier{}, and the third between the \receiver{}  and the \courier{}.
The result is the courier $\func{system}$ defined below.
\begin{align*}
  & \func{carry} \; in0 \; in1 \; out \; =  \recv{in0 }{} 
  \recv{(\suc \; in1) }{} 
  \send{(\suc \suc \; out) }{\suc \constr{0}} 
  \send{(\suc \suc \; out) }{\constr{0}} \PO \\
  & \func{system} =  \new{} ( \func{send} \; \constr{0} 
  \comp{}{\new{} ( \func{send} \; \constr{0} } 
  \comp{}{\new{} ( \func{recv} \; \constr{0} } 
  \comp{}{\func{carry} \; (\suc \suc \constr{0}) \; (\suc \constr{0}) \; \constr{0}))) } 
\end{align*}

@@

%%
\clearpage
\bibliographystyle{splncs04}
\bibliography{paper}

%%
\clearpage
\appendix
\changetext{}{10em}{-5em}{-5em}{}\input{appendix.tex}
\end{document}
